\bf Aggregated Financial Forecasting Calculation in Human-Computer Distributed Computing

### 2020-04-02 Aggregated-Financial-Forecasting-Calculation-in-Human-Computer-Distributed-Computing/paper.tex
Some more text was added.

This research proposes financial forecasting calculation based on users classification and votes given for particular financial future event. The rest of this paper is organized as follows: Section 2 describes the problems related to financial forecasting; Section 3 states the ideas for computing in a distributed environment; Section 4 proposes a practical solution for a mobile distributed voting solution; Section 5 reveals some practical experiments and related results; and Section 6 concludes with some suggestions for further work.
%
\section{Financial Time Series}
%
\section{Distributed Computing in Forecasting}
%
\section{Android OS Crowdsensing Solution}
%
\section{Experiments \& Results}
%
\section{Conclusions}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

@@

>>>>

This research proposes financial forecasting calculation based on users classification and votes given for particular financial future event. The rest of this paper is organized as follows: Section 2 describes the problems related to financial forecasting; Section 3 states the ideas for computing in a distributed environment; Section 4 proposes a practical solution for a mobile distributed voting solution; Section 5 reveals some practical experiments and related results; and Section 6 concludes with some suggestions for further work.
%
\section{Financial Time Series}
%
Time series are values measured in strict time order \cite{time-series-01}. In most of the cases, measurements are done in equal time intervals, but exceptions also do exist \cite{time-series-02}. The result of such measurements is discrete time-ordered data. There are many natural processes that can be described with time series as average daily temperature, count of sunspots number of flu sick people, values of the prices and many others \cite{time-series-03}. Time series are useful in almost every domain where measurements can be done in temporal order. Line charts are the most used tool for visualization of time series.

Technical analysis of financial time series uses a group of methods for temporal data analyzing in such a way that meaningful statistics and other characteristics to be extracted. Financial time series forecasting is based on a model that predicts future values according to previously observed values. Financial time series usually have trend, seasonality and high-frequency oscillations \cite{time-series-04}. The base of the technical analysis in financial time series is an appropriate curve fitting to the points which are already known.
%
\section{Distributed Computing in Forecasting}
%
\section{Android OS Crowdsensing Solution}
%
\section{Experiments \& Results}
%
\section{Conclusions}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

@@

\bibitem{time-series-01} Bandt, C., Pompe, B.: Permutation Entropy A Natural Complexity Measure for Time Series. Physical Review Letters, \textbf{88}(17), 174102 (2002)

\bibitem{time-series-02} Salvador, S., Chan, P.: Toward Accurate Dynamic Time Warping in Linear Time and Space. Intelligent Data Analysis, \textbf{11}(5) 561--580 (2007)

\bibitem{time-series-03} Lan, Y.: Computational Approaches for Time Series Analysis and Prediction Data-Driven Methods for Pseudo-Periodical Sequences. University of Bradford (2009)

\bibitem{time-series-04} Kolev, K., Sevova, J., Ketipov, R., Blagoev, I., Petrov, P., Kostadinov, G., Zankinski, I.: Removal of Linear Component and Sinusoidal Harmonics from Time Series with Differential Evolution. Proceedings of Annual University Scientific Conference of Vasil Levski National Military University, 1586--1594 (2019)
